Efficient Coalition Formation for Web Services

### 2013-03-13 papers/coalition/coalition.tex
Changes

Over the past years, online services have become part of critical business services. The increasing reliance on web-based applications has significant implications for service providers which calls for a seamless integration of business process, applications and web services of the Internet. Web services as a highly available software function accessible at a network address over the web, usually provid a set of stateless functions. Delivering high quality services on the dynamic and unpredictable nature of Internet is a critical and challenging task.

@@

Most of the recent work on communities of services are either user-centric and focus user satisfaction \cite{Chun02user-centricperformance} or there are many works in distributed, grid, cluster and cloud computing which are system-centric and focus on system throughput and performance and utilization of the system. However in real world environments both users and services are selfish and self-interested agents, aiming to maximize their own profit. In real world environments, both these parties will participate and collaborate as long as its economically efficient for them.

Recently, \cite{DBLP:conf/IEEEscc/LimTMB12, DBLP:conf/IEEEscc/KhosravifarABT11} have proposed mechanisms in which try to maximize gain for both parties. A two-player non-cooperative game theory method between web services and community manager was proposed in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. The strategies for a web service when facing a new community, is requesting to join or refusing the invitation to join the community and the set of strategies for communities are inviting the web service or refusing the web service join request. Both parties based on their capacity, market share and reputation will have different set of utilities over the strategy profiles of the game. The problem with this method is the game is between community master and the new web service, and all other web services already residing within the community are ignored. Those web services can lose utility and gain having to collaborate with new web services, they may deviate and join other communities if they are unsatisfied. In \cite{DBLP:conf/IEEEscc/LimTMB12} a 3-Way satisfaction selection approach has been proposed. In their approach, they proposed a web service selection process for community masters catering for the efficiency of 3 parties of users, web services and communities. In this work, they show how the gains of these parties are coupled together and they suggest a linear optimization process for optimizing the needs of the 3 parties. However, the optimization problem in this solution tends to optimize some parameters considering all web services even if they are weak. There are no clear thresholds for accepting or rejecting new web services. The optimization result for example could suggest web services already residing within the community to increase or decrease their capacity to adjust with weakness of other parties in the system. However, a strong performing web service could deviate anytime it finds itself unsatisfied within the community instead of adjusting its service parameters.

In this paper, we proposed a cooperative game theory based model for aggregation of web services within communities. The solution concepts of cooperative game theory seeks to find most efficient ways of forming coalitions (teams) of agents, maximizing their gain and payoff, and also distributing gain in a fair way to keep coalitions stable by having all agents satisfied. We first propose a representation function for communities of web services based on their qualities and capacities. Using this function we can evaluate the $worth$ of each coalition of web services. Our community managers facing new membership requests, analyses whether the new coalition having the new set of web services will keep the community stable for $all$ web services already residing in the community or not. The community manager will reject the membership requests if it finds out new coalition can be unstable since there can be $any$ subset of web services gaining significantly more by deviating, colluding with new web services and joining other communities. Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and gain more, they will form new coalitions with other communities. The cooperative game theory solution methods are combinatorial in nature and are NP-complete, making them impractical in real world applications; however, using the concepts of group stability we have offered approximation algorithms running in polynomial time providing web services and community owners with applicable and near-optimal decision making mechanisms.

The rest of paper is organized as follows. Section \ref{s:preliminaries} describes architecture and parameters and some basic cooperative game theory concepts, section \ref{s:model} presents our solution model in three different scenarios. Section \ref{s:resutls} presents our experiments and results and finally section \ref{s:conclusion} concludes the paper and identified future work.

@@

This means in order to keep the characteristic function convex, new agents should have more marginal contribution as coalition size grows.

@@

As future work, we would like to perform more analytical and theoretical work on the convexity condition for the characteristic function on web service applications. It is possible to work on compact or succinct representation of our service model (i.e. a graph representation) to reduce the input complexity and solution concepts of cooperative game and membership checking algorithms. From web service aspect, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperating game theory concepts can be used in our scenario. The web services would stay and join communities as they wish, however, they would resolve the instability and unfairness issues by side payments.

>>>>

Over the past years, online services have become part of critical business services. The increasing reliance on web-based applications has significant implications for service providers which calls for a seamless integration of business process, applications and web services of the Internet. Web services as a highly available software function accessible at a network address over the web, usually provide a set of stateless functions. Delivering high quality services on the dynamic and unpredictable nature of Internet is a critical and challenging task.

@@

Most of the recent work on communities of services are either user-centric and focus on user satisfaction \cite{Chun02user-centricperformance} or they are system-centric and focus on system throughput and performance and utilization of the system. There are many contributions in distributed, grid, cluster and cloud computing services which are system-centric. However in real world environments both users and service providers are self-interested agents, aiming to maximize their own profit. In real world environments, both these parties will participate and collaborate as long as it's economic and efficient for both of them.

Recently, \cite{DBLP:conf/IEEEscc/LimTMB12, DBLP:conf/IEEEscc/KhosravifarABT11} have proposed mechanisms in which they try to maximize gain for both parties. A two-player non-cooperative game theory method between web services and community manager was proposed in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. The strategies for a web service when facing a new community, is requesting to join or refusing the invitation to join the community and the set of strategies for communities are inviting the web service or refusing the web service join request. Both parties based on their capacity, market share and reputation will have different set of utilities over the strategy profiles of the game. The problem suffers from ignoring many quality parameters and also ignoring the web services already residing within the community. The game is only between the community master and the new web service, and all other web services already residing within the community are ignored. Those web services can lose utility or payoff, having to collaborate with new web services. They may deviate and join other communities if they are unsatisfied, which is not addressed in their approach. In \cite{DBLP:conf/IEEEscc/LimTMB12} a 3-Way satisfaction selection approach has been proposed. In their approach, they have proposed a web service selection process for community masters catering for the efficiency of all three parties of users, web services and communities. In this work, they show how the gains of these parties are coupled together and they suggest a linear optimization process for optimizing the needs of the 3 parties. However, the optimization problem in this solution tends to optimize some parameters considering all web services even if they are weak. There are no clear thresholds for accepting or rejecting new web services. The optimization result for example could suggest web services already residing within the community to increase or decrease their capacity to adjust with weakness of other parties in the system. However, a strong performing web service could deviate anytime it finds itself unsatisfied within the community instead of adjusting its service parameters.

In this paper, we propose a cooperative game theory based model for aggregation of web services within communities. The solution concepts of cooperative game theory seeks to find most efficient ways of forming coalitions (teams) of agents, maximizing their gain and payoff, and also distributing gain in a fair way to keep coalitions stable by having all agents satisfied. We first propose a representation function for communities of web services based on their qualities and capacities. Using this function we can evaluate the $worth$ of each community of web services. Our community managers facing new membership requests, analyses whether the new coalition having the new set of web services will keep the community stable for $all$ web services already residing in the community or not. The community manager will reject the membership requests if it finds out new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more by deviating and joining other communities. Also web services facing communities, will try to join communities which maximizes their gain, if they find out they can deviate and gain more, they will form new coalitions with other communities. The cooperative game theory solution methods are combinatorial in nature and are NP-complete, making them impractical in real world applications; however, using the concepts of coalition stability we have offered approximation algorithms running in polynomial time providing web services and community managers with applicable and near-optimal decision making mechanisms.

The rest of paper is organized as follows. Section \ref{s:preliminaries} describes architecture and parameters and some basic cooperative game theory concepts, section \ref{s:model} presents our solution model in three different scenarios. Section \ref{s:resutls} presents our experiments and results and finally, section \ref{s:conclusion}, concludes the paper and identified future work.

@@

This implies in order to keep the characteristic function convex, new agents should have more marginal contribution as coalition size grows.

@@

As future work, we would like to perform more analytical and theoretical work on the convexity condition for the characteristic function on web service applications. It is possible to work on compact or succinct representation of our service model (i.e. a graph representation) to reduce the input complexity and solution concepts of cooperative game and core membership checking algorithms. From web service aspect, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperating game theory concepts can be used in our scenario. The web services would stay and join communities as they wish, however, they would resolve the instability and unfairness issues by side payments.
